HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-16 paper/main.tex
ddd

>>>>

\begin{tikzpicture}[semithick, x=2.4cm,y=0.8cm, >=latex, baseline=7ex,
      inner sep=.3ex, outer sep=.7ex, minimum size=1.2ex,->]
  \node (ROOT) [label={G}] [fill=green, circle] {}
  child {node [label={R}] {Golf} edge from parent node[left]  {$L$}}
  child {node [label={\#1}] {became} edge from parent node[left]  {$L$}}
  child {node [label={\#1}] {a} edge from parent node[left]  {$L$}}
  child {node [label={\#1}] {passion} edge from parent node[left]  {$L$}}
  child {node [label={\#1}] {for} edge from parent node[left]  {$L$}}
  child {node [label={\#1}] {his} edge from parent node[left]  {$L$}}
  child {node [label={\#1}] {oldest} edge from parent node[left]  {$L$}}
  child {node [label={\#1}] {daughter} edge from parent node[left]  {$L$}}
  child {node [label={\#1}] {,} edge from parent node[left]  {$L$}}
  child {node [label={\#1}] {she} edge from parent node[left]  {$L$}}
  child {node [label={\#1}] {attended} edge from parent node[left]  {$L$}}
  child {node [label={\#1}] {daily} edge from parent node[left]  {$L$}}
  child {node [label={\#1}] {lesssons} edge from parent node[left]  {$L$}}
  child {node [label={\#1}] {and} edge from parent node[left]  {$L$}}
  child {node [label={\#1}] {greatly} edge from parent node[left]  {$L$}}
  child {node [label={\#1}] {improved} edge from parent node[left]  {$L$}};

  \com{
  child {node (H1) [label={\#8}] [fill=black,circle] {}
    child {node [label={\#2}] {graduation} edge from parent node[right] {$P$}}
      %child {node {to Paris} edge from parent node[right] {$A$}}
      edge from parent node[left] {$H$}
    }
    child {node (H2) [label={\#9}] [fill=black,circle] {}
      child {node  {} edge from parent[draw=none]}
      child {node  {} edge from parent[draw=none]}
      child {node [label={\#3}] (Tom) {Tom} edge from parent node[right] {$A$}}
      child {node [label={\#4}] {moved} edge from parent node[right] {$P$}}
      child {node [label={\#10}] [fill=black,circle] {}
        child {node [label={\#5}] {to} edge from parent node[right] {$R$}}
        child {node [label={\#6}] {NYC} edge from parent node[right] {$C$}}
        edge from parent node[right] {$A$}}
      %child {node {to Paris} edge from parent node[right] {$A$}}
      edge from parent node[left] {$H$}
    };
    \draw (H1) -> (Tom) node[midway, right] {$A$ \hspace{0.2cm}};
    }
  \end{tikzpicture}
\caption{\label{fig:ucca_example2}
  Sample UCCA annotation. Edge labels mark UCCA categories. \#$<$index$>$ marks the node
indices.}
\end{figure}
